Peer-to-Peer 6502 Cellular Automata

### 2018-07-03 paper.tex
write

As well as writing the (volatile) state of the cell, a write operation can overwrite its 32K operating system
(mapped to address range \hexrange{8000}{FFEF} in the virtual machine; the last 16 bytes, corresponding to \hexrange{FFF0}{FFFF}, are ignored).
After the first time an operating system is used in the blockchain, it can be referred to by SHA-256 hash, to save space.

>>>>

As well as writing the (volatile) state of the cell, a write operation can overwrite the cell's 32K operating system
(mapped to address range \hexrange{8000}{FFEF} in the virtual machine; the last 16 bytes, corresponding to \hexrange{FFF0}{FFFF}, are ignored).
After the first time an operating system is used in the blockchain, it can be referred to by SHA-256 hash, to save space.
